Through the eyes of the teacher

### 2021-02-22 paper_1/paper_1_supplement_new_table.Rmd
update alpha

# create a basic table (tibble) using tidyverse functions for teachers' self assessment 
teacher.scale.quest.table <- quest.raw.data %>% # select data
  filter(perspective == "self-assessment")%>%
  group_by(scale) %>%
  summarise("M" = round(mean(value), 2),
            "SD" = round(sd(value), 2),
            "Min" = min(value),
            "Max" = max(value),
            "Skewness" = skewness(value),
            "Kurtosis" = kurtosis(value))

>>>>

# create a basic table (tibble) using tidyverse functions for teachers' self assessment 
# adding alpha column

teacher.scale.quest.table <- quest.raw.data %>% # select data
  filter(perspective == "self-assessment")%>%
  group_by(scale) %>%
  summarise("M" = round(mean(value), 2),
            "SD" = round(sd(value), 2),
            "Min" = min(value),
            "Max" = max(value),
            "Skewness" = skewness(value),
            "Kurtosis" = kurtosis(value))
